Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2020-05-06 article.tex
Separate MHC-I and MHC-II, resulting in a 2 state Markov chain
Add Holm-Bonferroni correction, describe number of expected significant results

To detect evolution, we determine the probability 
that all of the observed TMH mutations have arisen by chance,
with regards to being detected/presented by the immune system.
To do so, we calculate the probability of observing the complete
dataset, for which we need to calculate the probability 
of each individual mutation.

@@

To calculate the probability all of our observations happened by chance,
we view our experiment as a two-state Markov chain, as depicted in
figure \ref{fig:markov_chain}. The two nodes depict the
two possible detection state a polypeptide is in, which is
either undetected $U$, or detected $D$ by the immune system.
The edges depict the probability of a state transition by mutation,
for example, $p_{DU}$ denotes the probability that a detected
polypeptide mutates into an undetected one.
We focus on polypeptides that are TMH and we assume a mutation that 
renders the TMH non-functional as lethal.

\begin{figure}
  \centering
  \input{markov_chain_4_states.latex}
  \caption{
    State transitions in TMHs caused by mutations, with respect to the
    detection by the immune system. Any TMH is either in a detected, $D$, or
    undetected, $U$, state. Mutations cause state transitions with probability
    $p$. For example, $p_{DU}$ denotes the probability that a detected
    TMH mutates into an undetected one.
  }
  \label{fig:markov_chain}
\end{figure}

@@

Of the complete system, we test for each of the 12 state transitions (that is,
we do not test for mutations that result in the same state).
For each transition rate, we know the expected and observed number
of transitions. If the observed number of transitions is below the expected
value, we test for finding that (low) number of transitions or less.
If the observed number of transitions is above the expected
value, we test for finding that (high) number of transitions or more.
We use a significance level $\alpha$ of 5\%, because we have no prior
evidence. 
As we are testing 12 hypothesis, applying the Bonferroni correction results
in $\alpha_c = \frac{\alpha}{12}$.
If the probability of observing that few/many 
transition is below $\alpha_c$, we will state 
that this unlikely situation is most likely caused by natural selection.

>>>>

To detect evolution, we determine the probability 
that all of the observed TMH mutations have arisen by chance,
with regards to being detected/presented by the immune system,
per MHC class and haplotype.
Because we use \richel{X} MHC-I and \richel{Y} MHC-II haplotypes
for a significance level of 5\%, by chance we expect \richel{X+Y/20}
times to find a haplotype that is suggested to have selection working 
upon it.

@@

To calculate the probability all of our observations happened by chance,
we view our experiment as a two-state Markov chain, as depicted in
figure \ref{fig:markov_chain}. The two nodes depict the
two possible detection state a polypeptide is in, which is
either undetected $U$, or detected $D$ by the immune system.
The $D$ can be either detection by an MHC-I or MHC-II haplotype.
The edges depict the probability of a state transition by mutation,
for example, $p_{DU}$ denotes the probability that a detected
polypeptide mutates into an undetected one.
We focus on polypeptides that are TMH and we assume a mutation that 
renders the TMH non-functional as lethal.

\begin{figure}
  \centering
  \input{markov_chain_2_states.latex}
  \caption{
    State transitions in TMHs caused by mutations, with respect to the
    detection by the immune system. Any TMH is either in a detected, $D$, or
    undetected, $U$, state. Mutations cause state transitions with probability
    $p$. For example, $p_{DU}$ denotes the probability that a detected
    TMH mutates into an undetected one.
  }
  \label{fig:markov_chain}
\end{figure}

@@

Of the complete system, we test for each of the 12 state transitions (that is,
we do not test for mutations that result in the same state).
For each transition rate, we know the expected and observed number
of transitions. If the observed number of transitions is below the expected
value, we test for finding that (low) number of transitions or less.
If the observed number of transitions is above the expected
value, we test for finding that (high) number of transitions or more.
We use a significance level $\alpha$ of 5\%, because we have no prior
evidence.

As we are testing 12 hypothesis, 
we correct against type I errors (false positives), 
by applying the Holm-Bonferroni correction, 
resulting in \richel{here is just a normal Bonferroni correction, for now}
$\alpha_c = \frac{\alpha}{12}$.
If the probability of observing that few/many 
transition is below $\alpha_c$, we will state 
that this unlikely situation may be caused by natural selection.
